---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Laura H.



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
cces %>%
      group_by(ideo5) %>%
      mutate(new_ideo=as.factor(recode(ideo5,'1' = "Very liberal", '2'="Liberal", '3'="Moderate",
                   '4'="Conservative", '5'="Very conservative")), count=n()) %>%
  ggplot(aes(x=new_ideo, y=count, fill=new_ideo)) + 
    geom_bar(stat="identity",position="dodge") +
    labs(x="Ideology",y="Count",title="Respondant Ideology")  +
    theme(legend.position="none")
    
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
cces %>%
      group_by(pew_religimp) %>%
      mutate(new_ideo=as.factor(recode(ideo5,'1' = "Very liberal", '2'="Liberal", '3'="Moderate",
                   '4'="Conservative", '5'="Very conservative")),
             new_pew=as.factor(recode(pew_religimp,'1' = "Very imp.", '2'="Somewhat imp.", '3'="Not too imp.",
                   '4'="Not imp.")), count=n()) %>%
      select(pew_religimp,new_pew, count, new_ideo) %>%
    ggplot(aes(x=new_pew, y=count, fill=new_ideo)) + 
    geom_bar(stat="identity") +
    labs(x="Importance of Religion",y="Count",title="Importance of Religion by Ideology") +
    guides(fill=guide_legend(title="Ideology"))
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
x <- c("Amanda", "Betty", "Carol")
y <- c(1:6)
Grade <- runif(18,min=80, max=100)
new_dat <- expand.grid(Student=x, Semester=y)
new_dat$Grade <- Grade

ggplot(new_dat, aes(Semester, Grade, color=Student)) + 
  geom_path(size=0.8) +
  labs(title="Student Grades by Semester") +
  theme(legend.position="none") +
  facet_wrap(~Student) 

```
